\textbf{Preprinting Microbiology}

### 2017-11-21 submission/Schloss_PrePrints_mBio_2017.tex
Update ASM data

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, I downloaded the \emph{bioRxiv} on April
17, 2017. I chose to analyze \emph{bioRxiv} preprints because these
preprints are amenable for submission to ASM journals and there were
9,780 \emph{bioRxiv} preprints compared to the 2,911 preprints that were
available at \emph{PeerJ Preprint} on the same date. The code used to
analyze these preprints and the rest of this manuscript are available as
a reproducible GitHub repository at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
Among the 9,780 preprints on bioRxiv, 483 were assigned by the authors
into the Microbiology category. One limitation of the \emph{bioRxiv}
interface is the inability to assign manuscripts to multiple categories
or to tag the content of the preprint. For example, this manuscript
could be assigned to either the Microbiology or the Scientific
Communication and Education categories. To counter this limitation, I
developed a more permissive approach that classified preprints as being
microbiology-affiliated if their title or abstract had words containing
\emph{yeast}, \emph{fung}, \emph{viral}, \emph{virus}, \emph{archaea},
\emph{bacteri}, \emph{microb}, \emph{microorganism}, \emph{pathogen}, or
\emph{protist}. I identified 1,617 additional manuscripts that I
considered microbiology-affiliated. These microbiology-affiliated
preprints were primarily assigned to the Evolutionary Biology (N=283),
Bioinformatics (N=237), or Genomics (N=231) categories.

As the total number of preprints has grown exponentially since the
creation of \emph{bioRxiv}, submission of microbiology-affiliated
preprints has largely followed this growth (\textbf{Figure 1A}).
Although preprints are still relatively new, the collection of
microbiology-affiliated preprints indicates widespread experimentation
with the format and considerable geographic diversity. Reflecting the
relative novelty of preprints, 1,484 (85.5\%) corresponding authors who
submitted a microbiology-affiliated preprint (N=1,735 total) have posted
a single preprint and 4.6\% have posted 3 or more preprints.
Corresponding authors that have posted microbiology-affiliated preprints
are from 67 countries and are primarily affiliated with institutions in
the United States (46.2\% of microbiology-affiliated preprints), United
Kingdom (12.9\%), and Germany (4.6\%). As the preprint format matures,
it will be interesting to see whether the fraction of authors that post
multiple preprints increases and whether the geographic diversity
amongst those authors is maintained.

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 197
(9.3\%) had been commented on at least once and only 48 (2.3\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer-review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. In spite of
the lack of tradition within the scientific community to comment
publicly online about colleagues' research results, I am optimistic that
this will change given the possibilities of new media (e.g.~Twitter,
Facebook, blogs); the advantage of the centralized commenting is that it
is easier for the authors and others to integrate the feedback with the
preprint. It is possible that incentives for open commenting and
reviewing could shift the trend. Importantly, authors do appear to be
incorporating feedback from colleagues or editorial insights from
journals as 545 (25.9\%) microbiology-affiliated preprints were revised
at least once. Among the preprints posted prior to January 1, 2016,
31.3\% of the Microbiology category preprints, 35.6\% of the
microbiology-affiliated preprints, and 33.6\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics I sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, I found that the median number of times an abstract or
PDF had been accessed was 922 (IQR: 601 to 1446) and 301 (IQR: 155 to
549), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the general public, I obtained the
Altmetric Attention Score for each preprint (\textbf{Figure 1B}). The
Altmetric Attention Score measures the number of times a preprint or
paper is mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources; it does not include the number of
citations (41). A higher score indicates that a preprint received more
attention. Microbiology-affiliated preprints have had a median Altmetric
Attention Score of 7.6 (IQR: 3.2 to 16.6) and those of all preprints
hosted at \emph{bioRxiv} have had a median score of 7.7 (IQR: 3.1 to
16.2). For comparison, the median Altmetric Attention Score for articles
published in \emph{mBio} published since 2013 was 5.0 (IQR: 1.5 to
14.5). Of all scholarship tracked by Altmetric, the median Altmetric
Attention Score for preprints posted at \emph{bioRxiv} ranks at the 87
percentile (IQR: 75 to 94). A controversial, yet more traditional metric
of impact has been the number of citations an article receives. I
obtained the number of citations for the published versions of
manuscripts that were initially posted as preprints. To allow for a
comparison to traditional journals, I considered the citations for
preprints published in 2014 and 2015 as aggregated by Web of Science
(\textbf{Figure 1C}). Among the preprints that were published and could
be found in the Web of Science database, the median number of citations
was 9 (IQR: 3-19; mean: 17.1). For comparison, among the papers
published in \emph{mBio} in 2014 and 2015, the median number of
citations was 6 (IQR: 3-11; mean: 8.5). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that the science presented in preprints and the publications
that result from them are accepted by the microbiology community at a
level comparable to more traditionally presented research.

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
RJSONIO (v.1.3-0), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and
tidyr (v.0.6.0) packages. All journal policies and the information cited
using webpage links was current on April 21, 2017.

@@

\hypertarget{ref-ASAPbio}{}
13.. \url{http://asapbio.org/feb23}.

>>>>

\textbf{\emph{Metrics for microbiology-affiliated preprints.}} To
analyze the use of preprints, I downloaded the \emph{bioRxiv} on April
17, 2017. I chose to analyze \emph{bioRxiv} preprints because these
preprints are amenable for submission to ASM journals and there were
16,740 \emph{bioRxiv} preprints compared to the 2,911 preprints that
were available at \emph{PeerJ Preprint} on the same date. The code used
to analyze these preprints and the rest of this manuscript are available
as a reproducible GitHub repository at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
Among the 16,740 preprints on bioRxiv, 936 were assigned by the authors
into the Microbiology category. One limitation of the \emph{bioRxiv}
interface is the inability to assign manuscripts to multiple categories
or to tag the content of the preprint. For example, this manuscript
could be assigned to either the Microbiology or the Scientific
Communication and Education categories. To counter this limitation, I
developed a more permissive approach that classified preprints as being
microbiology-affiliated if their title or abstract had words containing
\emph{yeast}, \emph{fung}, \emph{viral}, \emph{virus}, \emph{archaea},
\emph{bacteri}, \emph{microb}, \emph{microorganism}, \emph{pathogen}, or
\emph{protist}. I identified 2,699 additional manuscripts that I
considered microbiology-affiliated. These microbiology-affiliated
preprints were primarily assigned to the Evolutionary Biology (N=400),
Bioinformatics (N=353), or Genomics (N=339) categories.

As the total number of preprints has grown exponentially since the
creation of \emph{bioRxiv}, submission of microbiology-affiliated
preprints has largely followed this growth (\textbf{Figure 1A}).
Although preprints are still relatively new, the collection of
microbiology-affiliated preprints indicates widespread experimentation
with the format and considerable geographic diversity. Reflecting the
relative novelty of preprints, 2,445 (84\%) corresponding authors who
submitted a microbiology-affiliated preprint (N=2,910 total) have posted
a single preprint and 5.5\% have posted 3 or more preprints.
Corresponding authors that have posted microbiology-affiliated preprints
are from 66 countries and are primarily affiliated with institutions in
the United States (49.4\% of microbiology-affiliated preprints), United
Kingdom (13.7\%), and Germany (4\%). As the preprint format matures, it
will be interesting to see whether the fraction of authors that post
multiple preprints increases and whether the geographic diversity
amongst those authors is maintained.

As stated above, preprints offer researchers the opportunity to improve
the quality of their work by adding a more formal and public step to the
scientific process. Among the microbiology-affiliated preprints, 313
(8.6\%) had been commented on at least once and only 58 (1.6\%) more
than three times using the \emph{bioRxiv}-hosted commenting feature.
Although the hosted commenting is only one mechanism for peer-review,
this result was somewhat disturbing since the preprint model implicitly
depends on people's willingness to offer others feedback. In spite of
the lack of tradition within the scientific community to comment
publicly online about colleagues' research results, I am optimistic that
this will change given the possibilities of new media (e.g.~Twitter,
Facebook, blogs); the advantage of the centralized commenting is that it
is easier for the authors and others to integrate the feedback with the
preprint. It is possible that incentives for open commenting and
reviewing could shift the trend. Importantly, authors do appear to be
incorporating feedback from colleagues or editorial insights from
journals as 951 (26.2\%) microbiology-affiliated preprints were revised
at least once. Among the preprints posted prior to January 1, 2016,
36.0\% of the Microbiology category preprints, 36.7\% of the
microbiology-affiliated preprints, and 33.9\% of all preprints have been
published. As noted above, not all authors submit their preprints to
journals. This would indicate that the ``acceptance rates'' are actually
higher. Regardless, considering that these acceptance rates are higher
than many peer-reviewed journals (e.g.~approximately 20\% at ASM
Journals), these results dispel the critique that preprints represent
overly preliminary research.

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics I sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, I found that the median number of times an abstract or
PDF had been accessed was 898 (IQR: 585 to 1428) and 0 (IQR: 0 to 0),
respectively. These values represent two aspects of posting a preprint.
First, they reflect the number of times people were able to access
science before it was published. Second, they reflect the number of
times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the general public, I obtained the
Altmetric Attention Score for each preprint (\textbf{Figure 1B}). The
Altmetric Attention Score measures the number of times a preprint or
paper is mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources; it does not include the number of
citations (41). A higher score indicates that a preprint received more
attention. Microbiology-affiliated preprints have had a median Altmetric
Attention Score of 7.7 (IQR: 3.1 to 16.6) and those of all preprints
hosted at \emph{bioRxiv} have had a median score of 8.1 (IQR: 3.1 to
16.5). For comparison, the median Altmetric Attention Score for articles
published in \emph{mBio} published since 2013 was 5.8 (IQR: 1.8 to
15.5). Of all scholarship tracked by Altmetric, the median Altmetric
Attention Score for preprints posted at \emph{bioRxiv} ranks at the 86
percentile (IQR: 74 to 93). A controversial, yet more traditional metric
of impact has been the number of citations an article receives. I
obtained the number of citations for the published versions of
manuscripts that were initially posted as preprints. To allow for a
comparison to traditional journals, I considered the citations for
preprints published in 2014 and 2015 as aggregated by Web of Science
(\textbf{Figure 1C}). Among the preprints that were published and could
be found in the Web of Science database, the median number of citations
was 14 (IQR: 6-26; mean: 26.7). For comparison, among the papers
published in \emph{mBio} in 2014 and 2015, the median number of
citations was 9 (IQR: 4-16; mean: 12.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that the science presented in preprints and the publications
that result from them are accepted by the microbiology community at a
level comparable to more traditionally presented research.

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.4.1).
Within R I utilized the cowplot (v.0.9.1), dplyr (v.0.7.0), ggplot2
(v.2.2.1), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.1.0),
RJSONIO (v.1.3-0), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
(v.0.7.1) packages. All journal policies and the information cited using
webpage links was current on April 21, 2017.

@@

\hypertarget{ref-ASAPbio}{}
13. ASAPbio awarded \$1 million from Helmsley Charitable Trust for
next-generation life sciences preprint infrastructure.
\url{http://asapbio.org/feb23}.
